Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
moved location of the figure
adjusted figure in readme again
updated readme

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- **`data-no-tank-rash.csv.zip` is a temporary fix file and needs to be deleted eventually!!!!**
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, **`data-no-tank-rash.csv.zip`**, and `figure-08-1.png.zip`).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

@@

@@

1. Knit paper (to make sure everything is up to date).
2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
3.

>>>>

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

@@

**Need to write still**

@@

1. Knit paper (to make sure everything is up to date).
2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
3. **Need to finish...**
